Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages

### 2015-09-10 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
formerly Bosch

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
\author{\IEEEauthorblockN{Thomas Bosch\IEEEauthorrefmark{1},
Benjamin Zapilko\IEEEauthorrefmark{1},
Joachim Wackerow\IEEEauthorrefmark{1}, 
Kai Eckert\IEEEauthorrefmark{2}} %and
%Eldon Tyrell\IEEEauthorrefmark{4}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}GESIS - Leibniz Institute for the Social Sciences, Mannheim, Germany\\
Email: \{firstname.lastname\}@gesis.org}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Stuttgart Media University, Stuttgart, Germany\\
Email: eckert@hdm-stuttgart.de}}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

>>>>

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
\author{\IEEEauthorblockN{Thomas Hartmann (formerly Bosch)\IEEEauthorrefmark{1},
Benjamin Zapilko\IEEEauthorrefmark{1},
Joachim Wackerow\IEEEauthorrefmark{1}, 
Kai Eckert\IEEEauthorrefmark{2}} %and
%Eldon Tyrell\IEEEauthorrefmark{4}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}GESIS - Leibniz Institute for the Social Sciences, Mannheim, Germany\\
Email: \{firstname.lastname\}@gesis.org}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Stuttgart Media University, Stuttgart, Germany\\
Email: eckert@hdm-stuttgart.de}}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
